Reduced diversity and increased specialization of Alaska salmon fishermen:

### 2016-10-14 salmon/paper/salmon_paper.Rmd
make plots

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy=FALSE, tidy.opts=list(width.cutoff=60), warning = FALSE, message = FALSE)
library(dplyr)
library(knitr)
library(ggplot2)
library(date)
library(ggtern)
library(reshape2)
library(mgcv)
library(fpc)
library(gridExtra)
library(glmmTMB)
library(zoo)
modelname = "model-linear" # model-linear-nointeractions
```

@@

@@

library(dplyr)
# plot proportion of species landed by salmon permit
g1 = group_by(cfec[cfec$p_fshy=="S 01A" & cfec$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p)) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("S01A") + theme(legend.position="none")

@@

```{r, echo=FALSE}
library(rstan)
```

>>>>

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy=FALSE, tidy.opts=list(width.cutoff=60), warning = FALSE, message = FALSE)
library(dplyr)
library(knitr)
library(ggplot2)
library(reshape2)
library(date)
library(ggtern)
library(mgcv)
library(fpc)
library(gridExtra)
library(glmmTMB)
library(zoo)
library(rstan)
modelname = "model-linear" # model-linear-nointeractions
```

@@

```{r, echo=FALSE, fig.pos="placeHere", fig.cap="Harvest of hatchery produced salmon through time and by area.", fig.height=3.2}

seak = read.csv("salmon/data-generated/stopha_table32.csv")
pws = read.csv("salmon/data-generated/stopha_table33.csv")
kodiak = read.csv("salmon/data-generated/stopha_table35.csv")

seak = melt(seak, id.vars = c("Year"))
pws = melt(pws, id.vars = c("Year"))
kodiak = melt(kodiak, id.vars = c("Year"))

seak$region = "Southeast"
pws$region = "Prince William Sound"
kodiak$region = "Kodiak"

seak$value[which(is.na(seak$value))] = 0
pws$value[which(is.na(pws$value))] = 0
kodiak$value[which(is.na(kodiak$value))] = 0

dat = bind_rows(seak, pws)
dat = bind_rows(dat, kodiak)

names(dat)[which(names(dat)=="variable")]="species"
dat$value = dat$value / 1000000

ggplot(dat, aes(Year, value)) +
  geom_area(aes(fill = species), position = "stack", colour = 1) +
  xlab("Year") + ylab("Harvest of hatchery produced salmon (millions)") +
  facet_wrap(~region, scale="free_y")

@@

# plot proportion of species landed by salmon permit
g1 = group_by(cfec[cfec$p_fshy=="S 01A" & cfec$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p)) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("S01A") + theme(legend.position="none")

@@
